\section{Introduction}

Problems in many-particle quantum mechanics is notoriously hard, and has over
many years resulted in a suit of methods and techniques for solving them
efficiently and reliably. A popular family of such methods is Variational
Monte-Carlo, which parameterize a trial wave function and seeks to optimize the
parameters in order to minimize the expected energy, thus approximating the
ground state of the system. While classic VMC methods, such as trial wave
functions with Jastrow factors, have proved useful, they come with some
weaknesses: the inflexibility of the trial wave function may lead to poor
approximations of the real ground state, even if a global minimum in energy for
the particular trial wave function was obtain. Further, observables are hard to
estimate from trial wave functions, because popular methods for sampling, such
as Metropolis-Hastings, tends to produce data with high degree of auto-correlation\cite{Blocking}. This
is even more true for larger systems, and leads to a high statistical
uncertainty in estimated observables. 

Drawing inspiration from Deep Learning, Artificial~Neural~Networks~(ANN) have in recent years been employed to model wave functions with great success\cite{pfau2019abinitio}.
Because of the huge number of parameters, ANNs tend to be
much more flexible than classical trial wave functions. However, there is the
new challenge to optimize the parameters, and the usual problem with
auto-correlated samples is still present. 

To address the latter problem, recent advances\cite{hibatallah2020recurrent,Sharir_2020} have  succeeded in
employing auto-regressive models on spin-systems, such as Quantum Ising-model.
To obtain a spin-configuration, each spin is sampled in sequence, each time
conditioning on the previous sampled spins. Because of the nature of
auto-regressive models, all sampled spin-configurations are uncorrelated,
removing the problem with high statistical variance in estimating observables. 

In this paper, we present an autoregressive model for bosonic quantum dots based
on Recurrent Neural Networks, inspired by the work of Hibat-Allah Et al. \cite{hibatallah2020recurrent}. 

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
